Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-04 ms.tex
major fix-up of correlation slope discussion

The primary FDS99 analysis considered the intrinsic grain properties, for 
example the emissivity power law indices, to be constant over the sky, and 
performed a correlation slope analysis to constrain these parameters with FIRAS
and DIRBE observations. FDS99 also constructed a DIRBE 240$\mu$m/100$\mu$m 
ratio to account for temperature variation at $\sim$1.3$^{\circ}$ resolution. 
In this work we seek to apply FDS99-like emission models to the \PLANCK~data 
set, which offers a dramatic enhancement in angular resolution relative to the 
FIRAS spectra. The \PLANCK~data thereby allow us to derive an improved 
temperature correction at near-\IRAS~resolution, re-evaluate the best-fit 
global dust properties, and fit additional parameters of the two-component 
model as a function of position on the sky.

@@

FDS99 determined the best-fit values of the two-component model global 
parameters $\beta_1$, $\beta_2$, $q_1/q_2$ and $f_1$ via a correlation slope
analysis incorporating DIRBE and FIRAS data. In this section, we seek to 
perform a correlation slope determination of these same global parameters, but
swapping the \PLANCK~HFI maps for FIRAS at low frequencies, while still 
relying on DIRBE at higher frequencies. We also seek to determine via this
correlation slope analysis whether or not the combination of \PLANCK+DIRBE data
favors two-component models over single-MBB models in the same way that the
FIRAS+DIRBE data did in the FDS99 analysis.

In the two-component model case, we wish to obtain estimates for six 
free parameters: $\beta_1$, $\beta_2$, $q_1/q_2$, $f_1$, $T_2$ and the overall 
spectrum normalization $n$. The constraints employ are the correlation
slopes of each of the \PLANCK~HFI bands, as well as DIRBE 100$\mu$m (3000 GHz),
140$\mu$m (2141 GHz) and 240$\mu$m (1250 GHz) against \PLANCK~857 GHz. We will 
refer to the slope for band $\nu_i$ as $s_{i,857}$. All of the correlations are
performed using $1^{\circ}$ smoothed maps. The slopes for \PLANCK~100-545 GHz 
are taken to be those from the relative zero level fits of 
\ref{sec:relzero}, and are illustrated by the dashed red lines in plots of 
Figure \ref{fig:dip}, right column. The 857 GHz slope is taken to be unity by 
definition. We use the SFD98 reprocessings of the DIRBE bands. Including 857 
GHz, we thus have 9 correlation slope constraints for six free parameters. 
Including DIRBE 140$\mu$m and 240$\mu$m is critical in making this problem 
sufficiently constrained, and also in providing information near the peak of 
the dust SED at $\sim$140$\mu$m, which is particularly sensitive to the 
presence of a single versus multiple MBB components. % last sentence mentioning
% that the large number of frequency channels and good coverage of the 
% dust SED peak were what made FIRAS so appropriate for FDS99 analysis ??

>>>>

The primary FDS99 analysis considered the intrinsic grain properties, for 
example the emissivity power law indices, to be constant over the sky, and 
performed a correlation slope analysis to constrain these parameters with FIRAS
and DIRBE observations. FDS99 also constructed a DIRBE 240$\mu$m/100$\mu$m 
ratio to account for temperature variation at $\sim$1.3$^{\circ}$ resolution. 
In this work we seek to apply FDS99-like emission models to the \PLANCK~data 
set, which offers a dramatic enhancement in angular resolution relative to the 
FIRAS spectra. The \PLANCK~data thereby allow us to derive an improved 
temperature correction at near-\IRAS~resolution, re-evaluate the best-fit 
global dust properties, and fit additional parameters of the two-component 
model as a function of position on the sky. % in this last sentence
% reference the relevant sections for each sub-goal mentioned

@@

FDS99 determined the best-fit values of the two-component model global 
parameters $\beta_1$, $\beta_2$, $q_1/q_2$ and $f_1$ via a correlation slope
analysis incorporating DIRBE and FIRAS data. Here we seek to estimate these 
same global parameters via an analogous correlation slope analysis in which we 
swap the \PLANCK~HFI maps for FIRAS at low frequencies, while still relying on 
DIRBE at higher frequencies. We also seek to determine via this correlation 
slope analysis whether or not the combination of \PLANCK+DIRBE data favors 
two-component models over single-MBB models in the same way that the 
FIRAS+DIRBE data did in the FDS99 analysis.

In the case of the two-component model, based on a spectrum of \PLANCK~and 
DIRBE correlations slopes, we wish to obtain estimates for six free parameters:
$\beta_1$, $\beta_2$, $q_1/q_2$, $f_1$, $T_2$ and the overall spectrum 
normalization $n$. The constraints we employ are the correlation slopes of each
of the \PLANCK~HFI bands, as well as DIRBE 100$\mu$m (3000 GHz), 140$\mu$m 
(2141 GHz) and 240$\mu$m (1250 GHz) relative \PLANCK~857 GHz, with 
\PLANCK~857 GHz considered the independent variable. We will refer to the slope
for band $\nu_i$ as $s_{i,857}$. All of the correlations are performed using 
$1^{\circ}$ smoothed maps. The slopes for \PLANCK~100-545 GHz are taken to be 
those from the relative zero level fits of \ref{sec:relzero}, and are 
illustrated by the dashed red lines in plots of Figure \ref{fig:dip}, right 
column. The 857 GHz slope is taken to be unity by definition. We use the SFD98 
reprocessings of the DIRBE bands. Including 857 GHz, we thus have nine 
correlation slope constraints for six free parameters. Including DIRBE 
140$\mu$m and 240$\mu$m is critical in making this problem sufficiently 
constrained, and also in providing information near the peak of the dust SED at
$\sim$140$\mu$m, which is particularly sensitive to the presence of a single 
versus multiple MBB components. % last sentence mentioning
% that the large number of frequency channels and good coverage of the 
% dust SED peak were what made FIRAS so appropriate for FDS99 analysis ??
